### 2015-03-02 fundamentals/impl.tex
removing sentences about testing the tests. I do think this is a very important point about QA and testing in general, but a bit too far into the weeds for this particular discussion, which needs to concisely focus on how cyclus has exceptional qa.
removing philosophical aside about how big a unit is. I do think this is well spoken and makes an important point about QA and testing in general, but again, I think it distracts somewhat from the focus on how cyclus has exceptional qa.

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign if the
simulator does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.

It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
just as likely to contain errors as the code it is designed to test.
However, it is assumed that diligence and one level of testing
is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
of testing-the-tests.

@@

Unit tests compare the results of the smallest code \emph{unit},
typically a single function or a class. What constitutes the smallest code
unit depends on the context of the specific unit in question. While this is
an ambiguous definition, when combined with a philosophy of keeping units as small
as possible, it is often clear in practice what needs to be tested.

\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.

>>>>

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign if the
simulator does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.  It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.

@@

Unit tests compare the results of the smallest code \emph{unit}, typically a
single function or a class.  \Cyclus uses the Google Test framework
\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
tests are required for any proposed change to the \Cyclus code base. Currently,
\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
cover approximately 65\% of their respective code bases, and these numbers are
expected to grow over time.
